### 2011-05-13 paper/paper.tex
kind of defined our testing conditions
Small edits

It is also shown in \cite{Smith} that the distributions from a Markov chain with a symmetric transition function eventually \emph{converge} to this stationary uniform distribution, provided that the probability distribution is nonzero everywhere. This is true for all of the methods we want to use except ball-walking. However, since our convex region $\mathcal{R}$ is connected, the distribution is positive everywhere if we consider our transition function to be the composition of sufficiently many steps. If the distribution for each $k^\text{th}$ step converge to the uniform distribution, for some $k$, then all the distributions will converge to the uniform distribution, since we can always apply the same argument, but shifted.

>>>>

It is also shown in \cite{Smith} that the distributions from a Markov chain with a symmetric transition function eventually \emph{converge} to this stationary uniform distribution, provided that the transition distribution of the Markov chain is nonzero everywhere. This is true for all of the methods we want to use except ball-walking. However, since our convex region $\mathcal{R}$ is connected, the distribution is positive everywhere if we consider our transition function to be the composition of sufficiently many steps. Then instead of considering one step of our Markov chain to be one iteration of ball-walking, we consider a single step to be the composition of a large number of iterations. In this case, we obtain a Markov chain with the same limiting behavior where the transition distribution is everywhere positive, so it converges to the stationary uniform distribution, and thus ball-walking must also.
